Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-11-26 jessie-writeup/jw-holes-clarified.tex
Reverted to original definition of embedding, defined R' with equivalent reports.

\begin{definition}
	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
	Let $\gamma$ and $\zeta$ be set-valued properties.
	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
\end{definition}

Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
\end{definition}

\begin{definition}
A property $\Gamma: \P \to \R$ is \emph{finite} if $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
\end{definition}

\begin{definition}
	A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior.
\end{definition}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets}

	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
	\jessie{(HOLE)-- double check/clarify the construction of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta} = \theta$, since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}).
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p) = \Gamma(p) \cap \R'$, so $\gamma$ is nondegenerate.

	\jessie{This next paragraph is definitely incomplete (HOLE)}
	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
	Thus, $\gamma$ is nonredundant.

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
\end{lemma}

\begin{proof}
	Let $\gamma: \P \toto \R'$, and $\Gamma: \P \toto \reals^d$.
	For contradiction, suppose there was some other nondegenerate, nonredundant $\zeta: \P \toto \R$ so that $\zeta \preceq \Gamma$.
	For any $\zeta \approx \gamma$, we know $\strip(\zeta) = \strip(\gamma)$.
	If $\zeta \not \approx \gamma$, there is no bijection from $\R$ to $\R'$, so then $\card(\R') \neq \card(\R)$.
	If $\card(\R') > \card(\R)$, then we either contradict nondegeneracy of $\zeta$ or nonredundancy of $\gamma$ and contradict nondegeneracy of $\gamma$ or nonredundancy of $\zeta$ with the other direction of inequality.
	Thus, we must have $\gamma \approx \zeta$, and conclude $\strip(\gamma)$ is unique.

@@

\begin{proof}[Proof Sketch]
	\emph{Uses: Conjecture~\ref{conj:gam-prime-exists}.}

	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.

@@

\begin{proof}
	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.

	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
	In the second case, for $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \gamma(p) \} = \gamma_{r'}$. 
\end{proof}

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ and $\R \subseteq \reals^d$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).  
  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.

  \end{enumerate}
\end{proposition}

@@

\item[$4 \implies 1$] 
Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.

\item [$1 \implies 5$]
Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of an embedding and assumption that $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\item [$2 \implies 3$]
	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_{r'}$ for $r' \in \reals^d$.
	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Conjecture~\ref{conj:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$.
	\jessie{(HOLE) - Why is this true?}

>>>>

%\begin{definition}
%	\jessie{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
%	Let $\gamma$ and $\zeta$ be set-valued properties.
%	We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
%\end{definition}

%Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ \footnote{Here, we slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.	($\phi$ is real valued, but we might be taking $\phi$ on every element of a set.)} for all $p \in \P$.
%\jessie{In hindsight-- not sure on this because of the extra dimension embedding counter example...}

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists an injection $\varphi:\R' \to \R$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$. %there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
\end{definition}

Note that we can take $\varphi^{-1}(r') = \{ r \in \R: \varphi(r) = r' \}$.
That is, we define the inverse of $\varphi$ as a possibly set-valued function.

\begin{definition}
A property $\Gamma: \P \to \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
\end{definition}

\begin{definition}
	A level set $\theta$ is \emph{full-dimensional} if it has nonempty interior.
\end{definition}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\jessie{Assumptions used: Finite FDLS}

	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
	\jessie{(HOLE)-- double check/clarify the construction of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \}$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.

	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	Therefore, we know that $\gamma(p) = [r]$ for all $p\in \P$.
	Since $[r]$ is well-defined for every report $r \in \R$, we know $\gamma$ is nondegenerate.

	Now to see $\gamma$ is nonredundant, first consider two level sets $r_1, r_2$ such that $\Gamma_{r_1} = \Gamma_{r_2}$.
	In this case, $[r_1] = [r_2] = r'$, so $\gamma_{r'} = \gamma_{r'}$ does not lead to a redundant report.

	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
	Suppose there are reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_{r'} \subsetneq \gamma_{r}$.
	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
	Therefore, if both $r$ and $r'$ are optimal on a set of positive measure, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes).
	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\Gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex. \jessie{Waved my hands at the bijection bit, come back and clarify.}
	Therefore, the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.

%	\jessie{This next paragraph is definitely incomplete (HOLE)}
%	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
%	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
%	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
%	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
%	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
%	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
%	Thus, $\gamma$ is nonredundant.

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma:\P\toto\R$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
\end{lemma}

\begin{proof}
	Let $\gamma:\P \toto \bar\R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
	We want to show $\strip(\gamma) = \strip(\Gamma')$.
	For each $\bar r \in \bar\R$, there is a set of reports in $S \subseteq \R$ so that there is a full-dimensional level set $\theta = \bigcap_{s\in S}\Gamma_s$ and $\bar r = [s]$ for every $s \in S$.
	For the same set of reports $S$, we can equivalently choose a different representative report $r' \in \R'$ so that $r' = [s]$ for every $s \in S$, since $\Gamma' \preceq \Gamma$.
	Therefore, there is a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$\footnote{Abusing notation for set $X$, $\varphi(X) = \{ \varphi(x) : x\in X \}$  } for all $p \in \P$.
	Therefore, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
\end{proof}

@@

\begin{proof}[Proof Sketch]
	\jessie{Uses: Conjecture~\ref{conj:gam-prime-exists}.}

	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional.

@@

\begin{proof}
	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
	For $\theta \in \strip(\Gamma)$, there is some report $r \in \reals^d$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
	Now consider the report $r' = [r]$.
	By definition, $r \in \Gamma(p) \implies [r] = r' \in \gamma(p)$.
	Therefore, there is some $r' \in \R$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
%	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
%	
%	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
%	In the second case, for $r \in \R$, we know $p \in \Gamma_{r} \implies p \in \{ p \in \P : r \in \Gamma(p) \cap \R \} = \{ p \in \P : r \in \gamma(p) \} = \gamma_{r}$. 
\end{proof}

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).  
  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.
  \end{enumerate}
\end{proposition}

@@

\item[$4 \implies 1$] 
Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).
For every $r' \in \R'$, let $\varphi(r') = \{ r\in\reals^d : r' = [r] \}$.
Then clearly for all $r \in \Gamma(p)$, we know $[r] = r' \in \gamma(p)$.
Additionally, we know that if $r' \in \gamma(p)$, then every equivalent report $r$ such that $[r] = r'$ as in $\Gamma(p)$, so $\Gamma$ embeds $\gamma$.
\jessie{Circular logic...}

\jessie{Define an injection, not a surjection...}

\item [$1 \implies 5$]
We know $\strip(\gamma) = \trim(\Gamma)$, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\item [$2 \implies 3$]
	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_{r'}$ for $r' \in \reals^d$.
	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Conjecture~\ref{conj:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
	\jessie{Waving my hands at this again, but same argument as the proof of Conjecture 1.}
